### 2016-12-04 sections/implementation.tex
Update on Overleaf.

\todo[inline]{Pokracovat vysvetlenim aproximace pomoci matice s nizsi hodnosti. Inspirovat se clankem \cite{SairaBanu2015}, pridat rovnice a diagram}

@@

$$\mtrx{A}=\mtrx{U_{1}}S_{1}\mtrx{V_{1}^{T}}+\mtrx{U_{2}}S_{2}\mtrx{V_{2}^{T}}+ ... +\mtrx{U_{n}}S_{n}\mtrx{V_{n}^{T}}$$

@@

$$\mtrx{A'}=\mtrx{U_{1}}S_{1}\mtrx{V_{1}^{T}}+\mtrx{U_{2}}S_{2}\mtrx{V_{2}^{T}}+ ... +\mtrx{U_{r}}S_{r}\mtrx{V_{r}^{T}}$$

@@

$$CR=\frac{r(m+n+1)}{m n}$$

@@

\todo[inline]{jak se pocita chyba; jak se da ridit maximalni chyba}

@@

>>>>

@@

\begin{equation}
\mtrx{A}=\mtrx{U_{1}}S_{1}\mtrx{V_{1}^{T}}+\mtrx{U_{2}}S_{2}\mtrx{V_{2}^{T}}+ ... +\mtrx{U_{n}}S_{n}\mtrx{V_{n}^{T}},
\label{eq:svd-expansion}
\end{equation}

@@

\begin{equation}
\mtrx{A'}=\mtrx{U_{1}}S_{1}\mtrx{V_{1}^{T}}+\mtrx{U_{2}}S_{2}\mtrx{V_{2}^{T}}+ ... +\mtrx{U_{r}}S_{r}\mtrx{V_{r}^{T}}.
\label{eq:svd-approx-expansion}
\end{equation}

@@

\begin{equation}
CR=\frac{r(m+n+1)}{m n},
\label{eq:cr-def}
\end{equation}

@@

Once the SVD decomposition is calculated for the result component there are two strategies how to proceed with the compression -- size or quality. Each strategy is assigned a control parameter that determines resulting compression ratio or approximation error.

\todo[inline]{Replace itemization with sub-sub-sections?}

\begin{itemize}
\item \textbf{compression ratio} -- If the focus is only on the size of compressed data, the rank $r$ of the approximation matrix can be calculated by the formula

\begin{equation}
r=\ceil*{CR \times \frac{m n}{m+n+1}},
\end{equation}

where $CR$ is the compression ratio, $0 \leq CR \leq 1$ ($0$ results in absolute compression while $1$ results in no compression).

\item \textbf{approximation error} -- In the usual case the most important parameter to take into account is the approximation error. Algorithm is trying to minimize the compression ratio while at the same time ensuring that predefined limit of approximation error is not exceeded. To quantify the error the Mean squared error ($MSE$) metric is used. To be able to compare different data-sets having different scales the normalized version of $MSE$ is used - Normalized root-mean-square deviation ($NRMSD$). Both metrics are defined in section \ref{sec:error}.

But how can be the rank of approximation matrix effectively calculated from the desired approximation error? Here comes handy the interesting property of the singular values:

\begin{equation}
\sum_{i=1}^{m} \sum_{j=1}^{n} (M_{ij})^{2} = \sum_{i=1}^{k}{\sigma_{i}^{2}},
\label{eq:elem-sqr-sigma-sqr}
\end{equation}

where $k=min(m, n)$, i.e. the smallest of two dimensions of the matrix $M$. From the above follows that the squared sum of elements of a matrix $M$ equals to the squared sum of its singular values $\sigma_{i}$. \todo{Reference to source or further explanation needed.} Using formulas \eqref{eq:svd-expansion} and \eqref{eq:svd-approx-expansion} the equation \eqref{eq:elem-sqr-sigma-sqr} can be applied to the difference between original matrix $A$ and approximation matrix $A'$:

\begin{equation}
\sum_{i=1}^{m} \sum_{j=1}^{n} (A_{ij} - A'_{ij})^{2} = \sum_{i=r+1}^{k}{\sigma_{i}^{2}},
\end{equation}

where the term on the right-hand side is the sum of squares of those singular values of the matrix $A$ that are cut away by the compression algorithm. The equation can be rewritten using the definition of $MSE$ in \eqref{eq:mse-def}:

\begin{equation}
MSE \times m n = \sigma_{r+1}^{2} + \sigma_{r+2}^{2} + ... + \sigma_{k-1}^{2} + \sigma_{k}^2.
\end{equation}

\begin{equation}
(NRMSD \times (X_{max}-X_{min}))^{2} \times m n = \sigma_{r+1}^{2} + \sigma_{r+2}^{2} + ... + \sigma_{k-1}^{2} + \sigma_{k}^2.
\end{equation}

\todo[inline]{Describe how to calculate rank of approximation matrix - take only the amount of singular values, that the value is lower than ...}

\end{itemize}

\todo[inline]{jak se pocita chyba; jak se da ridit maximalni chyba;}

@@

\begin{algorithm}
  \caption{Euclid’s algorithm}\label{euclid}
  \begin{algorithmic}[1]
    \Procedure{Euclid}{$a,b$}\Comment{The g.c.d. of a and b}
      \State $r\gets a\bmod b$
      \While{$r\not=0$}\Comment{We have the answer if r is 0}
        \State $a\gets b$
        \State $b\gets r$
        \State $r\gets a\bmod b$
      \EndWhile\label{euclidendwhile}
      \For{\texttt{<some condition>}}
        \State \texttt{<do stuff>}
      \EndFor
      \State \textbf{return} $b$\Comment{The gcd is b}
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

### 2016-12-04 sections/introduction.tex
results added
Update on Overleaf.

\section{Introduction}
\label{section:introduction}

The effort to reduce size of resulting data from complex finite element analyses to accelerate (or even make possible) post-processing using common personal computer is not new. In \cite{Benes2015} is presented one possible direction for research in this area -- the replacement of discrete data produced by finite element solver by simple continuous functions. These approximation functions can be then described be low number of parameters. The focus is on \textit{geometry}. The main goal is to find the areas in domain where the output discrete function has predictable development and can be easily replaced by e.g. linear continuous function. Although this approach has great results for some class of functions it is not applicable to problem in general. For some special cases, such as functions with discontinuities, the method has poor results because approximation error is too high and -- what is more important -- it can not be controlled in advance.

In this study the purely \textit{algebraic} approach is applied. ...

>>>>

\section{Introduction}
\label{sec:introduction}

% Introduction to field of FEM results post-processing. Description of all terms used.

The effort to reduce size of resulting data from complex finite element analyses to accelerate (or even make possible) post-processing using common personal computer is not new.
\todo[inline]{State of the art. Add references to work in this field.}
In \cite{Benes2015} is presented one possible direction for research in this area -- the replacement of discrete data produced by finite element solver by simple continuous functions. These approximation functions can be then described be low number of parameters. The focus is on \textit{geometry}. The main goal is to find the areas in domain where the output discrete function has predictable development and can be easily replaced by e.g. linear continuous function. Although this approach has great results for some class of functions it is not applicable to problem in general. For some special cases, such as functions with discontinuities, the method has poor results because approximation error is too high and -- what is more important -- it can not be controlled in advance.

In this study the purely \textit{algebraic} approach is applied.

\todo[inline]{Describe alternative methods for compression: e.g. discrete 9/7 bi-orthogonal wavelet transform, discrete cosine transform, Karhunen-Loeve transform, and combinations of these}

### 2016-12-04 sections/math.tex
results added
Update on Overleaf.

\section{Mathematical background}
\label{section:math}

Singular Value Decomposition in general

>>>>

\section{Mathematical background}
\label{sec:math}

\todo[inline]{Singular Value Decomposition in general}

% Describe how to calculate decomposition of arbitrary matrix with example

\subsection{Error estimation}
\label{sec:error}

\todo[inline]{Singular values and norms of matrix}

(following taken from \cite{SairaBanu2015})

Mean square error:
\begin{equation}
MSE=\frac{1}{m n} \sum_{i=1}^{m} \sum_{j=1}^{n} (A_{ij} - A'_{ij})^{2}
\label{eq:mse-def}
\end{equation}

where \textit{A} represents the original image and \textit{A'} represents the
reconstructed image of dimension $m \times n$.

Rooted Mean Square Deviation:
\begin{equation}
RMSD=\sqrt{MSE}
\label{eq:rmsd-def}
\end{equation}

Normalized Rooted Mean Square Deviation:
\begin{equation}
NRMSD=\frac{RMSD}{X_{max}-X_{min}}=\frac{\sqrt{MSE}}{X_{max}-X_{min}}
\label{eq:nrmsd-def}
\end{equation}

Peak signal to noise ratio [db]:
\begin{equation}
PSNR=10\log_{10}\frac{(X_{max}-X_{min})^{2}}{MSE}
\end{equation}

\begin{equation}
PSNR=20\log_{10}\frac{X_{max}-X_{min}}{\sqrt{MSE}}=20\log_{10}\frac{1}{NRMSD}
\end{equation}

\begin{equation}
PSNR=-20\log_{10}NRMSD
\label{eq:psnr-def}
\end{equation}

\subsection{Sparse matrix of details}

\subsection{Randomized SVD}
